---
title: "FW and ISt Combine"
author: "Lisa Vance"
date: "`r Sys.Date()`"
output: html_document
---

Code for combining Fremont Weir and I St stage data for inundation estimate

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Retrieve Fremont Weir and I St stage data from WDL:
   Select custom range - YBFMP monitoring starts 1998 and select through date range for publishing

  Fremont Weir(Station #A02170):
  https://wdl.water.ca.gov/WaterDataLibrary/StationDetails.aspx?Station=A02170&source=map

  I St(Station #A02100): https://wdl.water.ca.gov/WaterDataLibrary/StationDetails.aspx?Station=A02100&source=map

2. Packages
```{r setup, include=FALSE}
library(readr)
library(ggplot2)
library(lubridate)
library(rcompanion)
library(viridis)
library(dplyr)
library(ggthemes)
library(tidyverse)
library(rcartocolor)
library(tidylog)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
